Mergeable Types

### 2017-02-28 paper/implementation.tex
URL

We describe the realization of \name on top of a persistent
distributed store and the language extensions to enable and enforce
the constraints of the \name.

>>>>

We describe the
realization\footnote{\url{https://github.com/icfp2017/vml}} of \name on top of a persistent
distributed store and the language extensions to enable and enforce
the constraints of the \name.
